Solar wind predictions for the Parker Solar Probe orbit

### 2017-10-21 paperMVVB/sections/content.tex
integrated changes by MVVB

\section{Introduction}
%solar wind beginnings
From observations of cometary tail fluctuations \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun. With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1959 \citep{Gringauz1960,Neugebauer1966}.
%in situ spacecraft
The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}. Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}\textbf{, \hl{SOHO} \citep{Domingo1995}}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction. Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}. Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}. \textbf{The in situ solar wind measurements closest to the Sun to date were made by} the Helios mission. \textbf{Helios~1, launched in 1974, reached distances of \SI{0.31}{\au}. Helios~2, launched two years later, approached the Sun as close as} \SI{0.29}{\au} \citep{Rosenbauer1977}.
%Solar Probe Plus mission
The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia at a distance of 9.86~solar radii (\Rs), that is, \SI{0.0459}{\au} \citep{Fox2015}. This distance will be achieved through seven Venus gravity assists with orbital periods of 88--168~days. In its prime mission time 2018--2025 PSP provides 24~orbits with perihelia inside \SI{0.25}{\au} \citep{Fox2015}. Even its first perihelion, 93~days after launch in 2018, will take PSP to an unprecedented distance of \SI{0.16}{\au} (\SI{35.7}{\Rs}). In comparison, the ESA Solar Orbiter mission with a planned launch in February 2019 will have its closest perihelia at \SI{0.28}{\au} \citep{Muller2013}.

@@

%transition
For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well, \hl{but differ for the extreme values, mainly caused by CME events. } 
The simple lognormal fit functions underestimate the frequency of the solar wind parameters in their high value tails, except for the temperature’s tail which is \hl{overestimated} as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}. The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.

@@

%\subsection{SSN fitting}
\textbf{Next we create solar activity dependent analytical representations of the solar wind frequency distributions. This is achieved by shifting the median positions of the lognormal distributions as a linear function of SSN. To enable these shifts }, we add a linear SSN dependency to the median
\begin{align}
	x_\text{med}(ssn) &= a_\text{med} \cdot ssn + b_\text{med}\,,	\label{eq:median_with_ssn}
\end{align}
using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to transfer its SSN dependency:
\begin{align}
	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
\end{align}
\textbf{These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$. This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags for each parameter determined before, to profit from the higher correlation.} The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
\begin{table*}
	\caption{Resulting fit coefficients from the OMNI data fitting with \textbf{the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}. For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value. The listed SSN time lags are used for the fits.}}
	\label{tab:ssn_fit_parameters}
	\centering
	\begin{tabular}{l@{} c@{}
		S[table-format = 1.3(2)e+1]
		S[table-format = 1.4(2)]
		S[table-format = 1.3(2)e+1]
		S[table-format = +1.3(2)e+1]
		c c
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}	&\multicolumn{1}{c}{SSN lag}\\
		\cline{3-4}\cline{6-7}
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$}	&\multicolumn{1}{c}{Baseline $b_\text{med}$}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}	&\multicolumn{1}{c}{[years]}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--	&3\\
		\hline
		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}	&\multirow{2}{*}{3}\\
			&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&	&\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}

@@

\textbf{The radial dependencies of the key solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} measured by both Helios probes are plotted in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}, together with their median and mean values for different solar distances, calculated for the minimal distance resolution \SI{0.01}{\au} of the data set.}
\begin{figure*}
	\includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_b_skip.pdf}
	\caption{Helios hourly data plots of the four solar wind parameters over solar distance. The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well. The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}. The maximal velocities of CME events larger than \SI{800}{\km\per\s} are indicated with circles.}
	\label{fig:radial_fit_4_thesis_light_b_skip}
\end{figure*}
Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling. Therefore we use the power law function
\begin{align}
	x(r) = d\cdot r^e	\label{eq:power_function}
\end{align}
for the regression fit of the median and mean, with $r$ being the solar distance in astronomical units, $d$ the magnitude at \SI{1}{\au} and $e$ the exponent. The fits are weighted through the different data counts per bin.
%fit result table and figure
\textbf{The obtained coefficients for the median and mean power law fits ($d_\text{med}$, $e_\text{med}$, $d_\text{avg}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter} and their corresponding curves are shown in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.}
\begin{table*}
	\caption{Fit coefficients for the median and mean solar distance dependencies \textbf{(\ref{eq:power_function})} of the four solar wind parameters derived from the combined Helios~1 and 2 data. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The crossing distances indicate where the median and mean fits intersect each other. The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
	\label{tab:mean_median_fit_parameter}
	\centering
	\begin{tabular}{l
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	@{}c
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	S[table-format = 1.1(2)e1]
	S[table-format = 1.3]}
		\hline\hline
		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}	&\multicolumn{1}{c}{Yearly variation}\\
		\cline{2-3}	\cline{5-6}
			&\multicolumn{1}{c}{$d_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}	&\multicolumn{1}{c}{$\Delta e$}\\
		\hline
		Magnetic field	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
		Velocity	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}
% source year variation: fit_out_yearly_gradients_table_b_stats.txt

@@

		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean\tablefootmark{a}}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{Seasonal variation}\\

@@

		\multicolumn{2}{l}{Magnetic field}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}	&2.8\\
		\multicolumn{2}{l}{Density}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}	&3.6\\
		\multicolumn{2}{l}{Temperature}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}	&1.9\\

@@

		\multirow{2}{*}{Velocity}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
			&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\

@@

		\multicolumn{2}{r}{$W''_\text{II}$}	&4.13(13)\tablefootmark{b}	&4.47(11)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\

@@

		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
		\tablefoottext{b}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}

>>>>

\section{Introduction}
%solar wind beginnings
From observations of cometary tail fluctuations \citet{Biermann1951} inferred the presence of a continuous flow of particles from the Sun. With his theoretical solar wind model \citet{Parker1958} formulated the existence of the solar wind even before the first satellites measured it in situ in 1959 \citep{Gringauz1960,Neugebauer1966}.
%in situ spacecraft
The idea of a space mission flying through the solar corona dates back to the founding year of NASA in 1958 \citep{McComas2008}. Since then several space missions have measured the solar wind in situ at a wide range of heliocentric distances, in case of Voyager~1 as far away as \SI{138}{\au}\footnote{\url{https://voyager.jpl.nasa.gov/}} (July 2017), having even left the heliospause into interstellar space at a distance of \SI{121}{\au} \citep{Gurnett2013}.
\textbf{Various} spacecraft have provided a wealth of solar wind measurements near Earth’s orbit, with WIND \citep{Lepping1995,Ogilvie1995}\textbf{, SOHO \citep{Domingo1995}}, ACE \citep{Stone1998} and DSCOVR \citep{Burt2012} still orbiting around the L1 point \SI{1.5}{million\,\km} ahead of Earth in the sunward direction. Additional measurements at other solar distances were provided by planetary missions to Venus and Mercury, such as PVO \citep{Colin1980} or MESSENGER \citep{Belcher1991}. Ulysses was the first probe that orbited the Sun out of the ecliptic plane and thus could measure solar wind even at polar latitudes \citep{McComas1998}. \textbf{The in situ solar wind measurements closest to the Sun to date were made by} the Helios mission. \textbf{Helios~1, launched in 1974, reached distances of \SI{0.31}{\au}. Helios~2, launched two years later, approached the Sun as close as} \SI{0.29}{\au} \citep{Rosenbauer1977}.
%Solar Probe Plus mission
The NASA Parker~Solar~Probe\footnote{\url{http://parkersolarprobe.jhuapl.edu/}} (PSP), formerly Solar~Probe~Plus, with a planned launch date in mid 2018, will reach after six years in 2024 its closest perihelia at a distance of 9.86~solar radii (\Rs), that is, \SI{0.0459}{\au} \citep{Fox2015}. This distance will be achieved through seven Venus gravity assists with orbital periods of 88--168~days. In its prime mission time 2018--2025 PSP provides 24~orbits with perihelia inside \SI{0.25}{\au} \citep{Fox2015}. Even its first perihelion, 93~days after launch in 2018, will take PSP to an unprecedented distance of \SI{0.16}{\au} (\SI{35.7}{\Rs}). In comparison, the ESA Solar Orbiter mission with a planned launch in February 2019 will have its closest perihelia at \SI{0.28}{\au} \citep{Muller2013}.

@@

%transition
For the bulk of the solar wind these static lognormal functions describe the parameters' distributions well\textbf{. The abnormally high parameter values in the distribution functions can be attributed to shock/CME events in agreement with the results of the OMNI solar wind investigations by \citet{Richardson2012}.} The simple lognormal fit functions underestimate the \textbf{frequencies in} their high value tails, except for the temperature’s tail which is overestimated, as seen in the insets of Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}\textbf{, this appears to be because CMEs do not come with abnormally high temperatures.} The velocity's compositional lognormal fit only slightly overestimates its tail as seen in the inset of Fig.~\ref{fig:histogram_fits_V_a_zoom_dbl_paper_pdfplot}.
The slow and fast part contribute almost equally ($c \approx 0.5$) to the long-term velocity distribution function.

@@

%\subsection{SSN fitting}
\textbf{Next we create solar activity dependent analytical representations of the solar wind frequency distributions. This is achieved by shifting the median positions of the lognormal distributions as a linear function of SSN. To enable these shifts }, we add a linear SSN dependency to the median
\begin{align}
	x_\text{med}(ssn) &= a_\text{med} \cdot ssn + b_\text{med}\,,	\label{eq:median_with_ssn}
\end{align}
using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to transfer its SSN dependency:
\begin{align}
	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
\end{align}
\textbf{These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$. This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags for each parameter determined before, to profit from the higher correlation.} The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
\begin{table*}
	\caption{Resulting fit coefficients from the OMNI data fitting with \textbf{the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}. For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value. The listed SSN time lags are used for the fits.}}
	\label{tab:ssn_fit_parameters}
	\centering
	\begin{tabular}{l@{} c@{}
		S[table-format = 1.3(2)e+1]
		S[table-format = 1.4(2)]
		S[table-format = 1.3(2)e+1]
		S[table-format = +1.3(2)e+1]
		c c
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}	&\multicolumn{1}{c}{SSN lag}\\
		\cline{3-4}\cline{6-7}
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$}	&\multicolumn{1}{c}{Baseline $b_\text{med}$}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}	&\multicolumn{1}{c}{[years]}\\
		\hline
		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--	&0\\
%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--	&6\\
		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--	&3\\
		\hline
		\multicolumn{1}{l}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}	&\multirow{2}{*}{3}\\
		\multicolumn{1}{l}{\textbf{[\SI{e2}{\km\per\s}]}}	&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&	&\\
		\hline
	\end{tabular}
\end{table*}

@@

\textbf{The radial dependencies of the key solar wind parameters over the distance range \SIrange{0.29}{0.98}{\au} measured by both Helios probes are plotted in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}, together with their median and mean values for different solar distances, calculated for the minimal distance resolution \SI{0.01}{\au} of the data set.}
\begin{figure*}
	\includegraphics[width=18cm]{figures/radial_fit_4_thesis_light_b_skip.pdf}
	\caption{Helios hourly data plots of the four solar wind parameters over solar distance. The mean and median per \SI{0.01}{\au} data bin and their fit curves are plotted as well. The Helios data has a native distance resolution of \SI{0.01}{\au}, thus, to make the abundance visible in these plots, we added a random distance value of up to \SI{+-0.005}{\au}. The maximal velocities of CME events larger than \SI{800}{\km\per\s} are indicated with circles.}
	\label{fig:radial_fit_4_thesis_light_b_skip}
\end{figure*}
Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling. Therefore we use the power law function
\begin{align}
	x(r) = d\cdot r^e	\label{eq:power_function}
\end{align}
for the regression fit of the median and mean, with $r$ being the solar distance in astronomical units, $d$ the magnitude at \SI{1}{\au} and $e$ the exponent. The fits are weighted through the different data counts per bin.
%fit result table and figure
\textbf{The obtained coefficients for the median and mean power law fits ($d_\text{med}$, $e_\text{med}$, $d_\text{avg}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter} and their corresponding curves are shown in Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}.}
\begin{table*}
	\caption{Fit coefficients for the median and mean solar distance dependencies \textbf{(\ref{eq:power_function})} of the four solar wind parameters derived from the combined Helios~1 and 2 data. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The crossing distances indicate where the median and mean fits intersect each other. The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
	\label{tab:mean_median_fit_parameter}
	\centering
	\begin{tabular}{l
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	@{}c
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	S[table-format = 1.1(2)e1]
	S[table-format = 1.3]}
		\hline\hline
		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}	&\multicolumn{1}{c}{Yearly variation}\\
		\cline{2-3}	\cline{5-6}
			&\multicolumn{1}{c}{$d_\text{med}$}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}	&\multicolumn{1}{c}{$\Delta e$}\\
		\hline
		\textbf{Magnetic field [\si{nT}]}	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
		\textbf{Velocity [\SI{e2}{\km\per\s}]}	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
		\textbf{Density [\si{\per\cm\cubed}]}	&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
		\textbf{Temperature [\SI{e4}{\K}]}	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
		\hline
	\end{tabular}
\end{table*}
% source year variation: fit_out_yearly_gradients_table_b_stats.txt

@@

		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Exponent}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{Seasonal variation}\\

@@

		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.358(25)	&5.705(28)	&-1.662(11)	&\multicolumn{1}{c}{--}	&2.8\\
		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.424(33)	&6.845(47)	&-2.114(20)	&\multicolumn{1}{c}{--}	&3.6\\
		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&6.357(64)	&10.72(14)	&-1.100(20)	&\multicolumn{1}{c}{--}	&1.9\\

@@

		\multirow{2}{*}{\textbf{Velocity}}	&$W''_1$	&3.707(13)	&3.748(16)	&\multirow{2}{*}{0.0990(51)}	&\multirow{2}{*}{0.557(45)}	&\multicolumn{1}{c}{\multirow{2}{*}{0.17}}\\
		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}}	&$W''_2$	&5.26(13)	&5.42(11)	&	&	&\\

@@

			&$W''_\text{II}$	&4.13(13)\tablefootmark{a}	&4.47(11)\tablefootmark{a}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\

@@

		\tablefoottext{a}{Velocity median and mean \SI{1}{\au} values for the resulting function. Error estimates derived from the individual fit part errors.}
